Indexes measures for oak decline severity using phenotypic descriptors

### 2019-11-11 manuscript/figures.Rmd
updated DAI response surface plots

```{r PDI_response_surfaces,fig.height = 6,fig.cap='PDI response surfaces for simulated descriptor values from trained Random Forest models. All other descriptors were set at the values of those of the trees with the lowest PDI used for trainig the models',cache=TRUE}
source('../code/PDI_response_surfaces.R')
grid.arrange(PDI_response_plot$`a)`,PDI_response_plot$`b)`,PDI_response_plot$`c)`,PDI_response_plot$legend,nrow = 2,newpage = F)
```

>>>>

```{r PDI_response_surfaces,fig.height = 6,fig.cap='PDI response surfaces for simulated descriptor values from trained Random Forest models. All other descriptors were set at the values of those of the trees with the lowest PDI used for trainig the models'}
source('../code/PDI_response_surfaces.R')
grid.arrange(PDI_response_plot$`a)`,PDI_response_plot$`b)`,PDI_response_plot$`c)`,PDI_response_plot$legend,nrow = 2,newpage = F)
```

### 2019-11-11 manuscript/manuscript.Rmd
warnings and messages now not included. Sorted library loading errors
figures included within manuscript
updated DAI response surface plots

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r library_load}
source('../code/library_load.R')
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,cache = TRUE,warning = FALSE,message = FALSE)
```

```{r library_load,cache=FALSE}
source('../code/library_load.R')
```

```{r prep}
source('../code/data_prep.R')
```

@@

## Figures

```{r figures,child='figures.Rmd'}
```

## Checks
